Poincar\'e--Friedrichs constants over triangulated domains

### 2024-06-25 main.tex
Update on Overleaf.

% Copied from McIntosh paper 
Rewriting $B^{k}$ in the same way, we get
\begin{equation}\label{eq:Bogo}
    B^{k} u(x) = - \int_{\Omega} \,(x-a) \lrcorner \int_1^\infty t^{{k}-1}\,u\left( a+t(x-a) \right) \,dt\,da\;.
\end{equation}
If $u \in C^{\infty}_{c}(\bbR^{n},\Alt^{k})$, 
one sees that $B^{k} u$ is smooth with support in $\bbR^{n}\setminus\overline\Omega$, 
and that $B^{k} u(x) = 0$ unless $x \in \Omega$. 
Since $\Omega$ is convex, $u \in C^{\infty}_{c}(\Omega,\Alt^{k})$ implies $\supp B^{k} u \subset\Omega$, 
Since $\Omega$ is bounded, $u \in C^{\infty}_{\overline\Omega}(\bbR^{n},\Alt^{k})$ implies $\supp B^{k} u \subset\overline\Omega$. 
The fact that $B^{k}$ indeed maps 
$C^{\infty}_{c}(\bbR^{n},\Alt^{k})$ to $C^{\infty}_{c}(\bbR^{n},\Alt^{{k}-1})$ will be a the following theorem.

@@

>>>>

We introduce the operator $B^{k}$, which is
\begin{equation}\label{eq:Bogo} % TODO: rewrite 
    B^{k} u(x) = - \int_{\Omega} \,(x-a) \lrcorner \int_1^\infty t^{{k}-1}\,u\left( a+t(x-a) \right) \,dt\,da.
\end{equation}
If $u \in C^{\infty}_{c}(\bbR^{n},\Alt^{k})$, 
then $B^{k} u$ is smooth with support in $\bbR^{n}\setminus\overline\Omega$ and $B^{k} u(x) = 0$ when $x \notin \Omega$. 
Since $\Omega$ is convex, $u \in C^{\infty}_{c}(\Omega,\Alt^{k})$ implies $\supp B^{k} u \subset\Omega$, 
Since $\Omega$ is bounded, $u \in C^{\infty}_{\overline\Omega}(\bbR^{n},\Alt^{k})$ implies $\supp B^{k} u \subset\overline\Omega$. 
% The fact that $B^{k}$ indeed maps C^{\infty}_{c}(\bbR^{n},\Alt^{k})$ to $C^{\infty}_{c}(\bbR^{n},\Alt^{{k}-1})$ will be a the following theorem.

@@

\begin{align}
    v_0 + \langle v_k - v_0, v_{k-1} - v_0, \dots, v_1 - v_0 \rangle,
    \\
    \langle v_n - v_{k+1}, \dots, v_n - v_{n-1} \rangle + v_{0},
    \\
    v_0 + \sum_{i=1}^{k} \lambda_{i} ( v_i - v_0 ),
    \\
    v_0 + \sum_{i=k+1}^{n} \lambda_{i} ( v_n - v_i ),
    \\
    v_0 + \sum_{i=1}^{k} \lambda_{i} ( v_i - v_0 ) + \sum_{i=k+1}^{n} \lambda_{i} ( v_n - v_i ),
\end{align}
\begin{align}
    v_0 \left( 1 - \sum_{i=1}^{k} \lambda_{i} \right)
    +
    \sum_{i=1}^{k} \lambda_{i} v_i 
    +
    \sum_{i=k+1}^{n-1} \lambda_{i} v_n
    -
    \sum_{i=k+1}^{n-1} \lambda_{i} v_i
\end{align}
\begin{align}
    v_0 \left( 1 - \sum_{i=1}^{k} \lambda_{i} \right)
    +
    \sum_{i=1}^{k} \lambda_{i} v_i 
    +
    \sum_{i=k+1}^{n-1} (-\lambda_{i}) v_i
    +
    \sum_{i=k+1}^{n-1} \lambda_{i} v_n
\end{align}
